Study Level trends

### 2024-04-26 analysis/07_study_change.Rmd
Clean up how we think about change groups.

change_group_ses_desc <- change_group_count_ses %>%
   mutate(change_description = case_when(
    S == "pos" ~ "increase in species richness, sometimes leading to increase in functional richness", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" ~ "functional change independent of species richness change",
    n == 7 ~ "no change", 
    .default = NA
  ))
```

```{r}
no_change <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id, ~. == 0)) %>%
  left_join(meta_clean)

redundancy <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(S == "neg", SES_FRic == "0", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(meta_clean)

redundancy_gain <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(S == "pos", SES_FRic == "0", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(meta_clean)

evenness <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id & !SES_FEve, ~. == 0)) %>%
  left_join(meta_clean)

increase <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(Jaccard_base == "neg", S == "pos", SES_FRic == "pos", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(meta_clean)
```

>>>>

change_group_ses_desc <- change_group_count_ses %>%
   mutate(change_description = case_when(
    S == "pos" ~ "increase in species richness, sometimes leading to increase in functional richness", 
    S == "neg" ~ "loss of redundancy", 
    S == "0" ~ "functional change independent of species richness change",
    n == 7 ~ "no change", 
    .default = NA
  ))

usethis::use_data(change_group_ses_desc)
```

```{r}
change <-  change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(if_any(all_of(c("S", "Jaccard_base", "SES_FRic", "SES_FEve", "SES_FDiv")), ~. != 0))

no_change <- study_meta %>% filter(!study_id %in% change$study_id, study_id %in% model_output$study_id)

redundancy <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(S == "neg", SES_FRic == "0", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(study_meta)

redundancy_gain <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(S == "pos", SES_FRic == "0", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(study_meta)

evenness <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(across(!study_id & !SES_FEve, ~. == 0)) %>%
  left_join(study_meta)

increase <- change_groups %>% 
  mutate(study_id = as.integer(study_id)) %>%
  filter(Jaccard_base == "neg", S == "pos", SES_FRic == "pos", SES_FDiv == "0", SES_FEve == "0") %>%
  left_join(study_meta)
```
